# Communicating results
    
* Goals for today's class:
  * Regression tables
  * Save tables and figures

## Set-up
```{r,include=FALSE}
library(tidyverse)
library(haven)
library(modelsummary)
options(warn = -1) # suppress warning messages that do not disturb the program flow
```



## Load libraries
```{r,eval=F}
library(tidyverse)
library(haven)

install.packages("modelsummary") # regression table
install.packages("pandoc") # to save regression table to Word doc output
library(modelsummary)
```


## VDem

```{r}
vars <- c("country_name", "country_id", "year", 
          "v2x_corr","e_gdppc")

df <- read.csv("Project/VDem/VDem_post2000.csv") |>
  dplyr::select(all_of(vars)) |>
  filter(year==2009) 
```


### Scatter plot the bivariate relationship {-}
```{r}
ggplot(data=df,aes(x=v2x_corr,y=e_gdppc)) +
  geom_point()
```

### Regression line {-}
```{r}
ggplot(data=df,aes(x=v2x_corr,y=e_gdppc)) +
  geom_point(size=1,alpha=.5) +
  geom_smooth(method="lm",size=.5) + # linear model, i.e. linear regression
  scale_y_continuous(breaks=c(seq(-5,100,by=10)))
```

#### Save ggplot as object {-}
```{r}
obj1 <- ggplot(data=df,aes(x=v2x_corr,y=e_gdppc)) + # assign ggplot to obj1
  geom_point(size=1,alpha=.5) +
  geom_smooth(method="lm",size=.5) + # linear model, i.e. linear regression
  scale_y_continuous(breaks=c(seq(-5,100,by=10)))
```

#### Using `ggsave` {-}
```{r}
# specify arguments `filename`, `plot`, `width` and `height` of image file
ggsave(filename = "regressionLine.png",
       plot = obj1,
       width=8, height=5)
```


### Regression table {-}

#### Regression output {-}
```{r}
m <- lm(data=df,e_gdppc ~ v2x_corr)

summary(m)
```


#### Table using `modelsummary` {-}
```{r}
modelsummary(m, stars=TRUE)
```

#### Goodness-of-fit statistics {-}
```{r}
get_gof(m)
```

#### Select relevant statistics {-}

* Keep only "number of observations", "R-squared", and "adjusted R-squared" values
```{r}
modelsummary(m, 
             stars=TRUE, 
             gof_map=c("nobs","r.squared","adj.r.squared")) # select relevant goodness-of-fit statistics
```

#### Relabel {-}
```{r}
modelsummary(list("Base"=m), # list allows me to name the models
             stars=TRUE,
             gof_map=c("nobs","r.squared","adj.r.squared"), 
             coef_rename=c("v2x_corr"="Corruption Index")) # rename coefficient
```


#### Save output {-}
Under Arguments > output, you can see a number of supported file formats: .docx, .html, .tex, .md, .txt, .csv, .xlsx, .png, .jpg
```{r}
?modelsummary
```


```{r,eval=F}
modelsummary(list("Base"=m),
             stars=TRUE,
             gof_map=c("nobs","r.squared","adj.r.squared"), 
             coef_rename=c("v2x_corr"="Corruption Index"),
             output="out.docx") 
```

### Clear environment {-}
```{r}
rm(list=ls())
```


## Canadian Election Study 2021

```{r}
vars <- c("cps21_age","cps21_news_cons","cps21_govt_confusing") #news consumption and internal political efficacy

ces_select <- read_dta("Project/CES2021/2021 Canadian Election Study v2.0.dta") |>
  dplyr::select(all_of(vars))
```

### Transform & drop NAs {-}
```{r}
ces_dropna <- ces_select |>
  mutate(cps21_govt_confusing=ifelse(cps21_govt_confusing==5, #conditional statement
                                     NA, #if yes
                                     cps21_govt_confusing), #if no
         cps21_news_cons=ifelse(cps21_news_cons==7, #conditional statement
                                NA, #if yes
                                cps21_news_cons)) |> #if no
  na.omit() #remove NAs
```

### Check transformed variables {-}
```{r}
table(ces_dropna$cps21_govt_confusing)

table(ces_dropna$cps21_news_cons)
```


### Regression table {-}
```{r}
m <- lm(data=ces_dropna,cps21_govt_confusing ~ cps21_news_cons) # model 1

summary(m)

modelsummary(list("Base"=m),
             stars=TRUE,
             gof_map=c("nobs","r.squared","adj.r.squared"), 
             coef_rename=c("cps21_news_cons"="News Consumption")) 
```

#### Controls {-}
```{r}
m2 <- lm(data=ces_dropna,cps21_govt_confusing ~ cps21_news_cons + cps21_age) # model 2

modelsummary(list("Base" = m,
                  "w/ Controls" = m2),
             stars=TRUE,
             gof_map=c("nobs","r.squared","adj.r.squared"), 
             coef_rename=c("cps21_news_cons" = "News Consumption",
                           "cps21_age" = "Age")) 
```


#### Save output {-}
```{r,eval=F}
modelsummary(list("Base" = m,
                  "w/ Controls" = m2),
             stars=TRUE,
             gof_map=c("nobs","r.squared","adj.r.squared"), 
             coef_rename=c("cps21_news_cons" = "News Consumption",
                           "cps21_age" = "Age"),
             output="ces.docx") 
```

### Clear environment {-}
```{r}
rm(list=ls())
```


## World Values Survey

```{r}
vars <- c("B_COUNTRY_ALPHA","Q73","Q236") #confidence in parliament, experts versus government

df <- read_rds("Project/WVS/WVS_Cross-National_Wave_7_rds_v6_0.rds") |>
  select(all_of(vars)) |>
  filter(B_COUNTRY_ALPHA=="CAN") # choice of country: Canada
```

### Transform & drop NAs {-}
```{r}
df_recode <- df |>
  mutate(Q73=ifelse(Q73<0,
                    NA,
                    Q73),
         Q236=ifelse(Q236<0,
                     NA,
                     Q236)) |>
  na.omit() # drops all rows with NA values
```

### Regression table {-}
```{r}
m <- lm(data=df_recode,
        Q236 ~ Q73)

summary(m)

modelsummary(list("Experts vs government"=m),
             stars=TRUE,
             gof_map=c("nobs","r.squared","adj.r.squared"), 
             coef_rename=c("Q73"="Confidence in Parliament"),
             output="wvs_regTable.docx") 
```

### Clear environment
```{r}
rm(list=ls())
```


## Asian Barometer
```{r}
vars <- c("country","Year",
           "q175","q169")

df <- read_dta("Project/asianbarometer_wave5/20230504_W5_merge_15.dta") |>
  select(all_of(vars)) |>
  filter(country==11) # Vietnam (refer to codebook)
```

### Transform & drop NAs {-}
```{r}
df_recode <- df |>
  mutate(q169 = ifelse(q169<1 | q169 > 4, NA, q169),
         q175 = ifelse(q175<1 | q175 > 4, NA, q175)) |>
  na.omit()
```

### Regression table {-}
```{r}
m <- lm(data=df_recode,
        q169 ~ q175)

summary(m)

modelsummary(list("Views toward Democracy"=m),
             stars=TRUE,
             gof_map=c("nobs","r.squared","adj.r.squared"), 
             coef_rename=c("q175"="US harm to Asia"),
             output="AB_regTable.docx") 
```

### Saving plots {-}
```{r}
df_recode |>
  ggplot(aes(fill=factor(q169),x=factor(q175))) +
  geom_bar(position="fill") +
  theme_bw() +
  scale_x_discrete(labels=c("Much more good","More good", "More harm", "Much more harm")) +
  xlab("US does more good or harm to Asia?") +
  ylab("Proportion") +
  scale_fill_manual(name="Democratic regimes full of problems", #legend label
                    values = c("navyblue","blue","skyblue","grey"), #color specification
                    labels = c("Strongly Agree","Somewhat Agree", "Disagree", "Strongly Disagree"))
```

#### Save ggplot as object {-}
```{r}
obj1 <- df_recode |>
  ggplot(aes(fill=factor(q169),x=factor(q175))) +
  geom_bar(position="fill") +
  theme_bw() +
  scale_x_discrete(labels=c("Much more good","More good", "More harm", "Much more harm")) +
  xlab("US does more good or harm to Asia?") +
  ylab("Proportion") +
  scale_fill_manual(name="Democratic regimes full of problems", #legend label
                    values = c("navyblue","blue","skyblue","grey"), #color specification
                    labels = c("Strongly Agree","Somewhat Agree", "Disagree", "Strongly Disagree"))
```

#### Using `ggsave` {-}
```{r}
# specify arguments filename and plot
ggsave(filename = "AB_x169y175.png",
       plot = obj1,
       height = 5, width = 8)
```

